### 2015-09-15 confl.tex
Text improvements, new example for conflict criterion

We define conflicting updates using minimal sequences made by the
update detector algorithm. Actually, we define conflicting \emph{pairs
of commands} since only two modifications can interfere with each other.
Later we will mark every command as a conflicting command if
it was a member of a conflicting pair.

Consider two commands, \(C_A(\pi)\in S_A\) and \(C_B(\gamma)\in S_B\) 
where \(S_A\) is the minimal sequence which
leads the original filesystem \(O\) to replica \(A\) and similarly,
\(S_B\) leads \(O\) to replica \(B\).

Now \(C_A\) and \(C_B\) are conflicting commands iff
\begin{center}
\((C_B\not\in S_A)\wedge(C_A\not\in S_B)\)\\\medskip
\emph{and} one of the following holds:\\\medskip
\begin{minipage}{12cm}
\begin{itemize}
\item \(\neg(C_A(\pi); C_B(\gamma) \eqifnbr C_B(\gamma); C_A(\pi))\)
 (they do not commute), \emph{or}
\item \(C_A(\pi); C_B(\gamma) \equiv break\), \emph{or}
\(C_B(\gamma); C_A(\pi) \equiv break\)\\(they break every
filesystem).
\end{itemize}\end{minipage}
\end{center}

We write \(C_1\confl C_2\) if \(C_1\) and \(C_2\) are conflicting
commands.
\begin{notrsi}
Clearly this relation is symmetrical i.e.,
\(C_1\confl C_2\implies C_2\confl C_1\).
\end{notrsi}

In appendix \ref{cbp:bp} we try to find a relation between this
definition and another one found in \BP.

>>>>

We define conflicting updates using minimal sequences provided by an
update detector algorithm. More specifically, we define conflicting \emph{pairs
of commands} since only two modifications can interfere with each other.
Later, every command will be marked as conflicting if it is a member of a
conflicting pair.

Let us consider two commands, \(C_A(\pi)\in S_A\) and \(C_B(\gamma)\in S_B\) 
where \(S_A\) is the minimal sequence which
leads the original filesystem \(O\) to replica \(A\) and similarly,
\(S_B\) leads \(O\) to replica \(B\).

Now \(C_A\) and \(C_B\) are conflicting commands iff
\begin{center}
\((C_B\not\in S_A)\wedge(C_A\not\in S_B)\)\\\medskip
\emph{and} one of the following holds:\\\medskip
\begin{minipage}{12cm}
\begin{itemize}
\item \(C_A(\pi); C_B(\gamma) \neqifnbr C_B(\gamma); C_A(\pi)\)
 (they do not commute), \emph{or}
\item \(C_A(\pi); C_B(\gamma) \equiv break\), \emph{or}
\(C_B(\gamma); C_A(\pi) \equiv break\)\\(they are equivalent to \(break\);
from which we know they break every filesystem).
\end{itemize}\end{minipage}
\end{center}

We write \(C_1\confl C_2\) if \(C_1\) and \(C_2\) are conflicting
commands.
\begin{notrsi}
Clearly this relation is symmetrical, i.e.
\(C_1\confl C_2\implies C_2\confl C_1\).
\end{notrsi}

In appendix \ref{cbp:bp} we determine the relation between this
definition and another one found in \BP.

### 2015-09-15 theorems.tex
Text improvements, new example for conflict criterion

\subsection{Soundness theorem}
\label{theorem:soundness}
In order to be able to use our algebra,
we must show that an algebraic relation between sequences also means
that the sequences act the same on filesystems.
%
It can be proven that for every two sequences of commands
\(S\) and \(S^*\) 
\begin{gather*}
\forall F: S\equiv S^* \implies SF=S^*F,\\
\forall F: (S\eqexp S^*)\wedge(SF\ne\ud)\implies SF=S^*F.
\end{gather*}
The proofs for the two cases are very similar. We use induction on the
number of times the inference rules are applied to the sequences.
The soundness of each individual law
(by investigating individual cases)
and that of the inference rules are shown separately.
For the detailed proof see Appendix \ref{app:theosound}.

@@

In the proof we define \emph{minimal sequences} in the following way:
Consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would hold
by definition).

>>>>

\subsection{Soundness theorem}
\label{theorem:soundness}
In order to be able to use our algebra,
we must show that an algebraic relation between sequences also means
that the sequences act the same on filesystems.
%
It can be proven that for every two sequences of commands
\(S\) and \(S^*\) 
\begin{gather*}
S\equiv S^* \implies \forall F: SF=S^*F,\\
S\eqexp S^* \implies \forall F: (SF\ne\ud \implies SF=S^*F).
\end{gather*}
The proofs for the two cases are very similar. We use induction on the
number of times the inference rules are applied to the sequences.
The soundness of each individual law
(by investigating individual cases)
and that of the inference rules are shown separately.
For the detailed proof see Appendix \ref{app:theosound}.

\medskip\noindent{\small{As special consequences of the soundness theorem, we know
that both \(S\equiv break\)
and \(S\eqexp break\) means that \(S\) breaks all filesystems.
--- EC, 2015
}}

@@

In the proof we define \emph{minimal sequences} in the following way:
Consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would
hold).
